Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
evaluation
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52652 72bbbca6-d526-0410-a7d9-f06f51895060

\section{Evaluation}

>>>>

\section{Evaluation}
For the Evaluation procedure, we follow the footsteps of the CoNLL-2000 shared task: dividing text into syntactically related non-overlapping groups of words. This chunking mechanism \cite{tjong2003introduction} is very similar to ours, in terms of words which only belong to one category (here, language), and also evaluation based on the phrase structure present in the data. The chunks here are such that they belong to only one language. For example, the sentence below, shows the chunks as group of words in square brackets and their tagged language at the beginning in braces - \\

[ \{br\} ur pegsun nevez da dapout e montroulez d'ar 15 a viz kerzu ] [\{fr\} nouvel autocollant dispo à #morlaix le 15 décembre ! ] \\

For our current task, each of the texts have been limited to two languages i.e. the primary and the secondary language. Hence the type of chunking tags are limited to these.
